Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
recommend to delete FIXME
add notes on features

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version 0.12.0 FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
Each level of the factor vector will result in one partition.
Alternatively to supplying an external factor vector, the name of a feature (type `character`) present within the task can be supplied via argument `col`.

@@

The last method from the \pkg{blockCV} package, "environmental blocking", makes use of *k-means* clustering [@hartigan1979a] in a possibly multivariate space.
The user can select a variable via argument `feature` specifying which levels will be used to create clusters.
Hereby, k-means will use Euclidean distance for cluster creation.
Hence, the selected input variables should be of type numeric.
To avoid a potential bias introduced by features with high variance when selecting multiple features, all features are standardized by default.

>>>>

<!--JM: you might want to delete the FIXME-->
Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version 0.12.0 FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
Each level of the factor vector will result in one partition.
Alternatively to supplying an external factor vector, the name of a feature (type `character`) present within the task can be supplied via argument `col`.

@@

The last method from the \pkg{blockCV} package, "environmental blocking", makes use of *k-means* clustering [@hartigan1979a] in a possibly multivariate space.
<!--JM: pls rewrite next sentence. Do not use levels when you later on say the feature has to be numeric-->
The user can select a variable via argument `features` which specifies which levels will be used to create clusters.
Hereby, k-means will use Euclidean distance for cluster creation.
Hence, the selected input variables should be of type numeric.
To avoid a potential bias introduced by features with high variance when selecting multiple features, all features are standardized by default.
